The Weakly Nonlinear Magnetorotational Instability in a local geometry

### 2017-03-22 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
unnorm 128 Pm1E-2 run

\edit1{Here, we make a preliminary test of our weakly nonlinear theory by comparing it to direct numerical simulation. Using Dedalus, we  solved the full, nonlinear equations \ref{eqset1} - \ref{eqset4} with all parameters ($\reym$, $Q$) equal to their critical values except the background magnetic field, which we set to $B_0 = 1 + \epsilon^2$. We thus drive the system MRI unstable in the same way as in our theory. The computational requirements of low $\Pm$ simulations are quite intense in both time and space. Despite being virtually smooth, the solutions require a resolution of $192 \times 1536$ grid points at $\Pm = 10^{-2}$. Because the system has such a small growth rate, it takes hundreds of orbits for the system to reach saturation, as compared to the few orbits typical of high $\reym$ simulations \citep[e.g.][]{2007MNRAS.378.1471L}. As a result, we make our comparison at $\Pm = 10^{-2}$, which provides a good tradeoff between probing relatively low $\Pm$ while keeping the computational time for these exploratry simulations modest. }

>>>>

\edit1{Here, we make a preliminary test of our weakly nonlinear theory by comparing it to direct numerical simulation. Using Dedalus, we  solved the full, nonlinear equations \ref{eqset1} - \ref{eqset4} with all parameters ($\reym$, $Q$) equal to their critical values except the background magnetic field, which we set to $B_0 = 1 + \epsilon^2$. We thus drive the system MRI unstable in the same way as in our theory. The computational requirements of low $\Pm$ simulations are quite intense in both time and space. Despite being virtually smooth, the solutions require a resolution of $192 \times 1536$ grid points at $\Pm = 10^{-2}$. Because the system has such a small growth rate, it takes hundreds of orbits for the system to reach saturation, as compared to the few orbits typical of high $\reym$ simulations \citep[e.g.][]{2007MNRAS.378.1471L}. As a result, we make our comparison at $\Pm = 10^{-2}$, which provides a good tradeoff between probing relatively low $\Pm$ while keeping the computational time for these exploratory simulations modest. }
